Testing atlantisom: generate survey sampled length comps for California Current Atlantis

### 2019-05-14 visualization_Rmd/CCAStdSurvLengthCompTest.Rmd
vis lf sample CCA

---
title: "Testing atlantisom: generate survey sampled length comps"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'knitr', 'rmarkdown', 'tidyr', 'dplyr', 'ggplot2',
  'data.table', 'here', 'ggforce', 'ggthemes'
), 'packages.bib')
```

@@

This section uses the `atlantisom::create_survey()` and `atlantisom::sample_fish()` to get a biological sample dataset. From that dataset, several other functions can be run:

 *  age samples from `calc_stage2age` and `sample_ages`
 *  length samples from `calc_age2length` and `sample_lengths` (TO BE WRITTEN)
 *  weight samples from `calc_age2length` and`sample_weights` (TO BE WRITTEN)
 *  diet samples from `sample_diet`

Atlantis outputs numbers by cohort (stage-age) and growth informtation, but does not output size of animals directly. The function we are testing here, `atlantisom::calc_age2length` converts numbers by cohort to a length composition. The [workflow originally envisioned](https://onedrive.live.com/?authkey=%21AFQkOoKRz64TLUw&cid=59547B4CB95EF108&id=59547B4CB95EF108%216291&parId=59547B4CB95EF108%216262&o=OneUp) was to create a survey, sample fish from the survey, then apply this function. We determined that it will not work better to create a length comp for the whole population, which could then be sampled. We rethought what we needed [here](https://sgaichas.github.io/poseidon-dev/RethinkSamplingFunctions.html) and test the new functions in this document.

### Standard survey settings for testing 
To create a survey, the user specifies the timing of the survey, which species are captured, the spatial coverage of the survey, the species-specific survey efficiency ("q"), and the selectivity at age for each species.

```{r sppgroups}

@@

```{r aggdens}

@@

```{r stdsurvey-lensamp, warning=FALSE, message=FALSE}

@@

```{r stdsurvey-calcage2length, warning=FALSE, message=FALSE}

@@

lfplot <- ggplot(atf_length_stdsurv$natlength, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte()

@@

## Samples for all species, then SAVE

@@

```{r allspplengthsamp, eval=FALSE}

@@

```{r moreplots, echo=TRUE}

@@

# add sample, this is census, probably want it first?
lfplot <- ggplot(mapping=aes(x=upper.bins)) +
  geom_bar(data=lf_census_prop, aes(weight = atoutput/totlen), fill="blue") +
  geom_bar(data=lf_samp_prop, aes(weight = atoutput/totsamp), colour="red") +
  theme_tufte()

>>>>

---
title: "Testing atlantisom: generate survey sampled length comps for California Current Atlantis"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'knitr', 'rmarkdown', 'tidyr', 'dplyr', 'ggplot2',
  'data.table', 'here', 'ggforce', 'ggthemes'
), 'packages.bib')
```

@@

Full methods are explained [here](https://sgaichas.github.io/poseidon-dev/StdSurvLengthCompTest.html).

To create a survey, the user specifies the timing of the survey, which species are captured, the spatial coverage of the survey, the species-specific survey efficiency ("q"), and the selectivity at age for each species.

```{r sppgroups, echo=TRUE}

@@

```{r aggdens, echo=TRUE}

@@

```{r stdsurvey-lensamp, warning=FALSE, message=FALSE, echo=TRUE}

@@

```{r stdsurvey-calcage2length, warning=FALSE, message=FALSE, echo=TRUE}

@@

lfplot <- ggplot(atf_length_stdsurv$natlength, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=paste(scenario.name, atf_length_stdsurv$natlength$species))

@@

## Samples for all species from SAVED file

@@

```{r allspplengthsamp, eval=FALSE, echo=TRUE}

@@

```{r moreplots}

@@

# add sample, this is census, probably want it first?
lfplot <- ggplot(mapping=aes(x=upper.bins)) +
  geom_bar(data=lf_census_prop, aes(weight = atoutput/totlen), fill="blue") +
  geom_bar(data=lf_samp_prop, aes(weight = atoutput/totsamp), colour="red") +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=paste(scenario.name, lf_census_prop$species))
